A large-scale study of polymorphism in R

### 2019-03-16 paper/main.tex
minor
mior
talked a bit about corpus, added some code stuff

\begin{abstract}
The R programming language is widely used in a variety of scientfic domains
for tasks related to data science. The language was designed to favor an
interactive style of programming with minimal syntactic and conceptual
overhead. This design is well suited to support interactive data analysis,
but is not well suited to generating performant code or catching programming
errors.  In particular, R has no type annotations and all operations are
dynamically checked at runtime. The starting point for our work is the
question: \emph{what could a static type system for R look like?}  To answer
that question we study the polymorphism that is present in over X millions
of lines of R code, XX packages, written over a period of Y years by Z
programmers.  We perform a dynamic analysis, leveraging tests and use-cases,
to determine the level of polymoprhism that is present in the code. We do
this for several potential notions of types. Our result suggest that
polymorphism is important in some key parts of the system but that
relatively simple type annotations could be used to capture most of the
interesting cases.
\end{abstract}
\maketitle

@@

>>>>

\begin{abstract}
The R programming language is widely used in a variety of scientfic domains
for tasks related to data science. The language was designed to favor an
interactive style of programming with minimal syntactic and conceptual
overhead. This design is well suited to support interactive data analysis,
but is not well suited to generating performant code or catching programming
errors.  In particular, R has no type annotations and all operations are
dynamically checked at runtime. The starting point for our work is the
question: \emph{what could a static type system for R look like?}  To answer
that question we study the polymorphism that is present in over X millions
of lines of R code, XX packages, written over a period of Y years by Z
programmers.  We perform a dynamic analysis, leveraging tests and use-cases,
to determine the level of polymorphism that is present in the code. We do
this for several potential notions of types. Our result suggest that
polymorphism is important in some key parts of the system but that
relatively simple type annotations could be used to capture most of the
interesting cases.
\end{abstract}
\maketitle

@@

%
%
%
%
\subsection{The Corpus}

\AT{I'm hesitant to go into too much detail here, as I'm not sure if we're quite done running our analysis.
I can imagine a scenario where we will try to rerun with a longer timeout just to get a little bit more data (because why not).}

We ran our analysis over a subset of CRAN, the Comprehensive R Archive Network.
We analyzed \AT{over 7500} packages, over half of all packages available on CRAN.
Our analysis had an explicit timeout of \AT{30 minutes} per package, as a number of R packages feature functions which have a nigh-eternal running time (e.g., machine learning packages and complex simulations) \AT{cite those packages/examples}.

\AT{Should we talk about some of the packages?
What else do we have to say about the corpus?
We can restate the numbers from the abstract.}
